Thesis Draft

### 2015-10-21 chapter1.tex
puzzle notebook.
Former-commit-id: 9d9397215989fa8018a50262946fbe342928ce75
artwork, statement, questions and debates
Former-commit-id: 9897c39b89687a410855e37f69f9464f07e3199e
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab

\chapter{Introduction}
Some text...

% This written portion was to evaluate the project in terms of a justificatory theoretical framework.

% So what is the issue here?

% Title: Trash as a Medium.

% Subsection: the purpose of this study
% Subsection: overview of chapters

% This question “what the future of photography would be like” is the main motivator of this thesis and the visual project is based on.

% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda.

% The project aims to what? and what needs to justify what it questions?

>>>>

\chapter{Introduction}

%****************************************
% Structure of this chapter
% Section: topic and its significance
% Section: the purpose of this study
% Section: overview of chapters

The topic and its significance \ldots

\section{Purpose of this study}
The aim of this study is \ldots

\section{Overview of Chapters}
Following chapter focuses on trash in theoretical aspects.

Third chapter seeks the root of using trash in the artworks and looks through the sample artworks.

Fourth chapter explains the project that supports this thesis. It's stages, approach to the topic mentioned here.

Finally last chapter offer an overall conclusion of this thesis.

%****************************************
% About the thesis statement and focus:
% Is it too broad?
% Is it debatable? Is is fact? (Trash is not a end point of objects, there is a life waiting for them?)
% What is my side? throwing away is required for society to go further? or omitting the tons of possibilities... 
% Supporting claims?
% What is my thesis statement? Again same topic... It needs to be solved...

%****************************************
% Examples from other thesis.
% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology. // The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art). It is questioned the role of art in transformation of discarded items. This thesis follows the discussions of what is waste and the states of waste or meaning of waste. Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.

%****************************************
% Sample phrases:
% The discussions (mentioned discussion are also formed the thesis project entitled ... )
% Aim of this thesis is ...
% There has been a recent spate of artistic work focusing on (over-)consumption using the lens of disposal and discard.
% as a reaction to the consumerist society.

%****************************************
% Some comments
% This written portion was to evaluate the project in terms of a justificatory theoretical framework.
% This question “what the future of photography would be like” is the main motivator of this thesis and the visual project is based on.
% Burada önemli olan şey soru veya sorgulanan şey. Bu soru projeye yön verecek. Yazılı tez ise bunun doğrulamasını, üretilen işin kavramsal ve kuramsal çerçevesini belirleyecek. Tartışmalar ne üzerine olmalı bu durumda. 
% The project aims to what? and what needs to justify what it questions? 
% At this point, the question of what will be in the future of photography has to be asked. Bu çok önemli, bir şeyler hazırlayıp neyin sorgulanması gerektiğini sormak gerekli.

% Tipografi ve ideoloji arasında bir ilişki vardır. Fotoğrafın geleceği? Kelime ve imaj arasındaki ilişki, beden ve algı üzerinden incelenebilir? kelime ve imaj arasında bir problme olduğundan bahsediyor. Sanat işlerinde çöp kullanmak toplum tarafından atılan şeyi tekrar kullanılabileceğini gösterebilir. Toplum ve çöp nispeten bir problemli bir durum. Burada bir dert var. Atılan tüketilen manalar var. Sanat bunları provoke mi ediyor. Peki ya ben ne öneriyorum, yani aslında bir şey önermem mi gerekiyor? Sanat ve çöp arasında nasıl bir ilişki vardır? Çöp ile diğer nesneler arasında nasıl bir ilişki vardır?

% Zaten hali hazırda sanatçılar bunu yapıyorlar, tez aslında bunları inceliyor olabilir ama tez aslında benim işimi inceliyor. iş neyi soruyor ise aslında tez de onu soruyor. Yapılan işlerle sorulan sorular arasında bir bağlantı var. Bu noktada aslında benim işin neyi sorguladığını bulmam gerekli. Çöp dönüştürülebilir, sanatsal bağlamda. (Çok geniş değil mi abi sanatsal bağlamda demek? Çöp de çok geniş bir konu.) Konuyu bir şeklide daraltmak gerekli.

% çöpe yeni bir alternatif yaşam üretmek gerekli. Aslında hepimiz bir şeyleri dönüştürüyoruz. Agnes varda aslında neyi anlatıyor: Toplayıcılık hala devam ediyor, bu toplayıcılar arasında snatçıları da geziyor, çünkü onlar da topluyorlar. Onlar da o çöplerde farklı şeyler görüyorlar. Kendi de mesela çöpe atılmış bir şeye anlam yüklüyor. Kendisininde aslında bir toplayıcı olduğunun farkına varıyor.

% Çöp ve dönüşüm, dönüşümün aşamaları... Başka sanatçıların methodlarını incelemek pek mantılı değil, onun dışında başka bir şey bulmam gerekli.

### 2015-10-21 chapter2.tex
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab

%%
%%
\subsection{Origins of Words}
The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?

@@

@@

% TODO not sure for this section, maybe mentioned above...
\subsection{My terminology selection}
(I use this word for this and that?)

@@

%
\subsubsection{Cycle of trash}
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. [REF. MIT Garbage project] Lots of different people touches to trash. With the trash what moves?

@@

%
\subsubsection{Examined-life, Zizek}
(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from
our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

%
\subsubsection{Perspectives related with trash from different disciplines}
This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it handled by the municipals generally.
\item Technological perspectives
\end{itemize}

@@

%
\subsubsection{Throw away culture}
Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?) Behavioral pattern of throw away culture results in the trash. (This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.

@@

%
\subsubsection{How does it become trash?}
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%
\subsubsection{Types and Comparison of trashes}
The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages.

@@

%
\subsubsection{What is wrong with trash?}
Relationship between entropy (second law of thermodynamics) and waste. Resources of nature turns to waste that it can revert it. Creating that are reversible again is problematic through the nature of sustainability. What is produced after it is consumed become worthless.

@@

@@

\section{Summary}
What can be extracted from all these words?

\begin{itemize}
\item Shared practice through the different ages of humanity and different societies. 
\item Moving nature of trash.
\item Classification, not the related with the object property. 
\item Value creation, shifts in the society. 
\end{itemize}

>>>>

%%
%%
\subsection{Origins of Vocabulary}
The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?

@@

% TODO other words, relation, comparasition etc.

@@

% TODO not sure for this section, maybe mentioned above...
I use word 'x' because \ldots (not sure for this.)

@@

%%
%%
\subsection{Cycle of trash}
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. [REF. MIT Garbage project] Lots of different people touches to trash. With the trash what moves?

@@

%%
%%
\subsection{Perspectives related with trash from different disciplines}
This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it handled by the municipals generally.
\item Technological perspectives
\end{itemize}

@@

%%
%%
\subsection{Throw away culture}
Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?) Behavioral pattern of throw away culture results in the trash. (This pattern does not consider recycling of it.) Artworks that are trying to raise awareness is related with this concept.

@@

In the scope of this thesis increasing consumption is motivator (draws attention more) but it does not bind to this. Always needed to keep in my mind that the practice of discard is not belongs to only current society.

%%
%%
\subsection{How does it become trash?}
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%
%%
\subsection{Types and Comparison of trashes}
The complexity of produced trashes of societies is increasing. For example developed countries that have nuclear plant generates radioactive wastes which highly hazardous for the environment is never exist previous societies. Think batteries and so on. Every society generates different types of wastes. Differs from country to country, society to society, ages to ages.

@@

The approach to the different type of trash will be different. In other word if trash is a result of classification of objects, it can be easily extracted that there is classification inside of it. There are some trashes that are more close to the people. More easy to convert them. more easy to regain to the society.

%%
%%
\subsection{What is wrong with trash?}
Relationship between entropy (second law of thermodynamics) and waste. Resources of nature turns to waste that it can revert it. Creating that are reversible again is problematic through the nature of sustainability. What is produced after it is consumed become worthless.

@@

%%
%%
\subsection{Examined-life, Zizek}
(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from
our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

@@

%%%
%%%
%%%
\section{Summary}
\begin{itemize}
\item Shared practice through the different ages of humanity and different societies. 
\item Moving nature of trash/objects.
\item Classification is the main key, trash is not related with the object property. 
\item Value creation, shifts in the society. 
\item Trash has archaeological value.
\item Trash has potential to be used again.
\end{itemize}

### 2015-10-21 chapter3.tex
reorganization
Former-commit-id: 05e9d1e6041cca1a5e5c185a3e09be73131053ab

\chapter{Trash as Medium (Trash in the Art)}

@@

%%%
%%%
%%%
\section{Collage, Assemblage and the Found Object}
In this chapter root of using objects in the artworks is examined. Using objects on artworks beyond their intended purpose. Developing artworks not only painting but also using paper and other stuff by pasting them together.

@@

%%
%% TODO reading...
\subsection{Art and activism}
Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.

\subsection{Recycling in the context of Art}
% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
Recycling has always been a common practice in the arts at least at a non-material level. From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole. Take and put. De-contextualize and re-contextualize. In that sense, art, as a system, is an act of recycling.

%%
%%
\subsection{Garbage Art}
"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts. This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}

%%
%% TODO change here
\subsection{History of Consumption and Waste}
"The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}

@@

%%
%% TODO sample statements here.
\subsection{Artist statements}

@@

%%
%%
\subsection{Artistic tactics}

@@

% junkyard art

@@

@@

% discussion is not collaboration, collaboration is used.

@@

% SketchBook Project. Inspires me a lot. Lots of works from all over the world. Full of creativity and showcase of richness of people's expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

@@

% In this thesis project case the issue is not the nature of art and its methods.

>>>>

\chapter{Trash in Art}

@@

%%%
%%%
%%%
\section{Root in the Art History}
In this chapter root of using objects in the artworks is examined. Using objects on artworks beyond their intended purpose. Developing artworks not only painting but also using paper and other stuff by pasting them together.

% TODO praphase
\textbf{[TODO praphrase]} "The use of trash as a fine art medium dates back at least to the work of early-20th-century artists such as Fortunato Depero and Kurt Schwitters. Use of found materials, including garbage, has been associated with assemblage art since the 1950s and has been practiced by other well-known artists, including graphic artist Christian Boltanski, sculptor Louise Bourgeois, and photographer Andres Serrano. Art made from garbage has since become much more common in fine arts venues such as museums, galleries, and high-profile installations, including H. A. Schuldt’s famous “Trash People,” which has traveled around the world since 1996." \cite{tauxe2012encyclopedia}

@@

%%
%% junkyard art
\subsection{Garbage Art, Recycling Art}
"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts. This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}

% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
Recycling has always been a common practice in the arts at least at a non-material level. From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole. Take and put. De-contextualize and re-contextualize. In that sense, art, as a system, is an act of recycling.

@@

%%
%% TODO sample statements here.
%\subsection{Artist statements}

@@

%*****************************************
% Maybe...
% Artistic tactics
% Topology of artworks
%*****************************************

@@

@@

%%
%% ACTIVISM as a methodology 
%% TODO reading...
\section{Art and activism}
Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.

@@

% why collaboration, is it really collaboration?

@@

%************************
% inspirational work.
% SketchBook Project. Inspires me a lot. Lots of works from all over the world. Full of creativity and showcase of richness of people's expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

@@

% In this thesis project case the issue is not the language of art and its methods.
